---
title: "Lab 10"
author: "Yehudis"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Your task is to obtain the data from the following paper and conduct a reproducible analysis of their results.

- Rosenbaum, D., Mama, Y., & Algom, D. (2017). Stand by Your Stroop: Standing Up Enhances Selective Attention and Cognitive Control. Psychological science, 28(12), 1864-1867.

- Note, the paper, the data, and an existing reproducible analysis of this data is available at https://crumplab.github.io/statisticsLab/lab-10-factorial-anova.html#important-stuff-4

- The re-analysis should focus only on Experiment 3. There are three main goals

  a. Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests (2 points)

  b. Reproduce a graph of the means, like shown in the paper (2 points)

  c. Present a power-curve analysis for the design. (2 points)
  
```{r}
library(papaja)
library(dplyr)
library(ggplot2)

#load data

all_data <- read.csv("Lab10.csv")

#Stand Stroop Effect

(stand_stroop <- t.test(all_data$incongruent_stand,
                        all_data$congruent_stand,
                        paired = TRUE))

#Sit Stroop Effect

(stand_sit<- t.test(all_data$incongruent_sit,
                        all_data$congruent_sit,
                        paired = TRUE))

```
 
```{r}
# Reproduction

# The Stroop effects in both the sitting condition, `r papaja::apa_print(sit_stroop)$full_result`, and the standing condition, `r papaja::apa_print(stand_stroop)$full_result`, were highly reliable

```

```{r}
stand_stroop_scores <- all_data$incongruent_stand-all_data$congruent_stand
sit_stroop_scores <- all_data$incongruent_sit-all_data$congruent_sit
  
stroop_differences <- sit_stroop_scores - stand_stroop_scores

(paired_results <- t.test(stand_stroop_scores,
                          sit_stroop_scores,
                          paired = TRUE))

(interaction_results <- t.test(stroop_differences))
```

```{r}
library(tidyr)

#convert to long

stroop_df <- all_data %>%
  pivot_longer(cols = 1:4,
               names_to = c("Congruency", "Posture"),
               names_sep = "_",
               values_to = "RTs")

#get means

overall_means <- stroop_df %>%
                  group_by(Posture,Congruency) %>%
                  summarize(meanRT = mean(RTs),
                            SEMRT = sd(RTs)/sqrt(length(RTs)))

#plot

ggplot(overall_means, aes(x=Posture,
                           y=meanRT,
                           group=Congruency,
                           fill=Congruency))+
  geom_bar(stat="identity",position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time (ms)")+
  geom_errorbar(aes(ymin=meanRT-SEMRT,
                    ymax=meanRT+SEMRT),
                position=position_dodge(width=.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(500,1000))
```

```{r}
#power curve

effect_sizes <- seq(0,1.5,.1)
prop_significant <-c()

for(i in 1:length(effect_sizes)){
  sim_ps <- replicate(1000, t.test(replicate(50, rnorm(1, effect_sizes[i], 1)),
                                   mu = 0)$p.value)
  
  prop_significant[i] <- length(sim_ps[sim_ps < .05])/1000
}

plot_df <- data.frame(effect_sizes,
                      prop_significant)

ggplot(plot_df, aes(x=effect_sizes,y=prop_significant))+
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks=seq(0,1.5,.1))+
  scale_y_continuous(breaks = seq(0,1.5,.1)) +
  ylab("Proportion Significant")
  
```


