---
title: "Lab4"
author: "Yehudis"
date: "9/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Estimate the letter occurrence probabilities of all 26 letters in English by measuring a paragraph of English text from wikipedia. (hint use strsplit() to split a paragraph into individual letters) (1 point).

```{r}
wikipedia <- "Ruth Bader Ginsburg (/ˈbeɪdər ˈɡɪnzbɜːrɡ/; born Joan Ruth Bader; March 15, 1933 – September 18, 2020),[1] also known by her initials RBG, was an American jurist who served as an associate justice of the Supreme Court of the United States from 1993 until her death in 2020. She was nominated by President Bill Clinton and was generally viewed as belonging to the liberal wing of the Court. Ginsburg was the second woman to serve on the U.S. Supreme Court, after Sandra Day O'Connor. During her tenure on the Court, Ginsburg authored notable majority opinions, including United States v. Virginia (1996), Olmstead v. L.C. (1999), and Friends of the Earth, Inc. v. Laidlaw Environmental Services, Inc. (2000)."

wikipedia_letters <- unlist(strsplit(wikipedia,split = ""))
lower_case <- tolower(wikipedia_letters)
letter_counts <- table(lower_case)
letter_counts <- as.data.frame(letter_counts)

library(dplyr)

final <- letter_counts %>%
  filter(lower_case %in% letters == TRUE)

total_letters <- sum(final$Freq)

final <- final %>%
  mutate(probabilities = Freq/total_letters)

knitr::kable(final)
```

2. Generate “random” strings of letters that are sampled from a distribution where letter occurrence probability is the same as natural English. Use the probabilities for each letter from this wikipedia article, or use your own estimates from the previous question (2 points).

```{r}

test_sample <- sample(final$lower_case, size = 3, replace = TRUE,
                      prob = final$probabilities)

my_letters <- sample(final$lower_case,50*5,replace=TRUE, prob = final$probabilities)

# turn the vector into a matrix with 5 columns
my_strings <- matrix(my_letters, ncol=5)

# each row is a word, need to collapse the column to create a string
paste(my_strings[1,], collapse="")
#> [1] "egyqg"

# loop to collapse all of the rows into words
random_strings <-c()
for(i in 1:dim(my_strings)[1]){
  random_strings[i] <- paste(my_strings[i,], collapse="")
}

random_strings

```


3. Generate a random walk of 10,000 steps. In a random walk, you are simulating the process of randomly taking a step up or down, as if you are on an infinite staircase. At each step you flip a coin. If you get heads you go up one step, if you get tails you go down one step. Start on step 0, then simulate a random walk for 10,000 steps. Your vector should preserve the step number for each step. For example, if the the first three steps were all heads, then the vector would begin with 0,1,2,3, which indicates a single step up each time. Plot the first 1,000 steps. (1 point)

```{r}

step <- c(0)
for(i in 1:10000){
  coin_flip <- sample(c(1,-1),1)
  step[i+1] <- step[i]+coin_flip
}

plot(step[1:1000])
```

4. What was the most positive and most negative step reached out of 10,000? (1 point)

```{r}
plot(step)
max(step)
min(step)
```

5. What was the longest run of steps where all steps were positive numbers. For example, in the sequence: 1,2,3,2,1,0,-1,-2,-1,-2,-1,0,1,2,3; the answer is 5 because the first five values were all positive, and this was the longest sequence of positive values. (1 point).

```{r}
logical_step <- sign(step)

sequence <-c()
counter <- 0
for(i in 1:length(logical_step)){
  if(logical_step[i] == 0){
    sequence <- c(sequence,counter)
    counter <- 0
  } else {
    counter <- counter+logical_step[i]
  }
}

max(sequence)
min(sequence)
```

