---
title: "Lab 9"
author: "Yehudis"
date: "11/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1 (A copy of this paper will be made available).

Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).

```{r}
(install.packages(rJava))

library(xlsx)
the_data <- xlsx::read.xlsx("lab9/When not choosing leads to not liking_Data.xlsx", sheetIndex = 1)

the_data <- read.csv(file="lab9/infant_choice_data.csv")

library(dplyr)

e1_data <- the_data %>%
  filter(ExperimentNumber == "1")

# binomial test

sum_C <- sum(e1_data$`Infant Chose C`)
total_C <- length(e1_data$`Infant Chose C`)

(binomial_p <- pbinom(q = total_C - sum_C,
                      size = total_C, prob = .5, lower.tail = TRUE)*2)

# chi-square by gender

library(tidyr)

gender_choice_table <- e1_data %>%
  group_by(Gender, `Infant Chose C`) %>%
  summarise(counts = n ()) %>%
  pivot_wider(names_from = c(Gender),
              values_from = counts)

gender_choice_table <- gender_choice_table[,2:3]

(gender_Xsq <- chisq.test(gender_choice_table))

uncorrected_Xsq <- 
  sum((gender_Xsq$observed-gender_Xsq$expected)^2/gender_Xsq$expected)

gender_Xsq_unc <- pchisq(uncorrected_Xsq,1,lower.tail = FALSE)

# chi-square for age

age_table <- e1_data %>%
  group_by(AgeMonths, `Infant Chose C`) %>%
  summarize(counts = n ()) %>%
  pivot_wider(names_from = c(AgeMonths),
              values_from = counts)

age_table[is.na(age_table)] <- 0
age_table <- as.matrix(age_table[,2:21])
(age_xs <- chisq.test(age_table))

age_xs$observed
age_xs$expected
```
#Original author results

However, in the critical test trial that followed, 16 of 21 infants (76.2%) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = .026, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, χ2(19, N = 21) = 18.24, p = .506, and χ2(1, N = 21) = 0.15, p = .696, respectively.

# Our reproducible results

However, in the critical test trial that followed, `r sum_C` of `r total_C` infants (`r sum_C/total_C`%) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = `.026,`r round(binomial_p,digits=3)` 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, $\chi^2$ (19, N = 21) = 18.24, p = .506, and $\chi^2$ (1, N = 21) = 0.15, p = .696, respectively.
